test plot resize

### 2018-05-10 inst/documents/rotations_notes.Rmd
pap3

@@

Write out some text explaining the story & maybe the order of the plots. (keep num plots manageable).

order could be
1. example plots
2. histograms 
3. violin plots
4.

Not sure how best to look at effect of inputs on rot_seq, rot, neither. I could bin input ranges and then look at proportions of the 3 within them ?

This would tell me how changing an input value changes the proportion of successes, failures and rot_only. Might be OK to display. Tricky to calculate, but again gets mired in the multivariate nature of the data & potential interactions.

If I go back to using a continuous variable of generations until thresholds I lose out on the successful results.

@@

Maybe reclass all 10k runs to succeed_both (2), succeed_rot (1), fail_both (0). Then see what are the best predictors of these ? Or do series of xy plots with points coloured, coloured points with all data will probably be a mess ...

>>>>

*10/5/18*

Testing setting width of plots for publication at 300 dpi into word doc.

Solution : just use fig.height & width (out.height etc not supported for word)
This makes the tiffs correct. Word foten resizes them. To get right in word, right click set size & position, just click reset to go back to 100%.

improved histogram figures

@@

@@
